---
title: "Medical Explorer V2"
output:
  flexdashboard::flex_dashboard:
    vertical_layout: fill
    orientation: rows
    theme: yeti
---


```{css}
.chart-wrapper {
  overflow-y: scroll;
}
```

   
```{r setup, include=FALSE}
library(tidyverse)
library(googlesheets4)
library(googledrive)
library(flexdashboard)
library(plotly)
library(kableExtra)
library(dplyr)
library(ggplot2)
library(lubridate)
library(plotly)
library(scales)
library("RColorBrewer")
library(timevis)
library(tufte)
library(stringr)
library(DT)
library(tidyr)
library(dplyr)
library(sparkline)
library(htmlwidgets)
library(formattable)
library(htmlwidgets)
library(purrr)
library(ggQC)
library(qcc)
library(patchwork)
library("ggTimeSeries")
#https://cran.r-project.org/web/packages/prettydoc/vignettes/tactile.html

cache="C:/Users/Leesah/Documents/Cache"

#Run this in the console before anything else to authenticate with google drive
#googledrive::drive_auth(use_oob = TRUE, email = "lisamaeanders@gmail.com",cache=cache)


#set global drive account
options(gargle_oauth_email = "lisamaeanders@gmail.com")

#connect using cached credentials
googledrive::drive_auth(email = "lisamaeanders@gmail.com",cache=cache)

#Make google sheets use the token from google drive
gs4_auth(token = drive_token())

drive_user()

#See here for more details on the approach used: https://gargle.r-lib.org/articles/non-interactive-auth.html#project-level-oauth-cache

#Load data from Google Drive
File = "https://docs.google.com/spreadsheets/d/1ycUwcrZkmSIh44YkqvTGOJWRjO2YmPvpJJcvorVof0U/edit#gid=932390330"

Records <- read_sheet(File, sheet = "Records")

Doctors <- read_sheet(File, sheet = "Doctors")

Medicines <- read_sheet(File, sheet = "Medicines")

History <- read_sheet(File, sheet = "History")

Thyroid <- read_sheet(File, sheet = "Thyroid")

Labs <- read_sheet(File, sheet = "Labs")

Temperature <- read_sheet(File, sheet = "Temperature")

Vitals <- read_sheet(File, sheet = "Vitals")

Limits <- read_sheet(File, sheet = "Limits")

Immunizations <- read_sheet(File, sheet = "Immunizations")

Period <- read_sheet(File, sheet = "Period")

Lisa_picture <- "MVIMG_20200402_143008.jpg"


#googledrive functions 
#googledrive::drive_find()
#googledrive::drive_get()

```


Lisa Anders {data-orientation=columns}
===================================== 

Column 
-------------------------------------

```{r}
#Placeholder for image

```

Hello! I developed this to better visualize my personal health data while I was going through some complicated medical evaluations. I hope you find this tool useful too.


```{r, out.width = "50%"}
#http://zevross.com/blog/2017/06/19/tips-and-tricks-for-working-with-images-and-figures-in-r-markdown-documents/
#include_graphics("https://en.wikipedia.org/wiki/The_Princess_Bride_(film)#/media/File:Princess_bride.jpg")
```




Vitals {data-orientation=rows}
=====================================

Rows 
-------------------------------------

### Age 

```{r}

birthday = "1989-07-30"

age = function(from, to) {
  from_lt = as.POSIXlt(from)
  to_lt = as.POSIXlt(to)

  age = to_lt$year - from_lt$year

  ifelse(to_lt$mon < from_lt$mon |
         (to_lt$mon == from_lt$mon & to_lt$mday < from_lt$mday),
         age - 1, age)
}

age = age(from = birthday,to = Sys.Date())

valueBox(value = age, icon = "far fa-hand-spock")
```

### Height

```{r}
currentHeight =paste0("5' 5",'"')

valueBox(value = currentHeight, icon = "fas fa-rocket")
```

### Weight

```{r}
Weight_v <- data.frame(Vitals) %>%
  filter(Test == "Weight") %>%
  rename("Weight" = "Value") %>%
  mutate(Weight = as.numeric(Weight)) 


last_weight =  Weight_v %>% 
  arrange(Date) %>% 
  mutate(previous_weight = lag(Weight, order_by = Date), Date =as.Date(Date)) %>% 
  mutate(Color = ifelse(Weight > previous_weight, "red", "green"),
         Difference = paste0(ifelse(Weight > previous_weight, "+", ""),round(Weight-previous_weight,1))) %>%
  arrange(desc(Date)) %>%
  head(1)
  
  currentWeight = paste0(last_weight$Weight, " (",last_weight$Difference, ") lbs")

valueBox(value = currentWeight, icon = "fas fa-robot")
```

### Blood Pressure

```{r}
last_bp =  Vitals %>% 
  arrange(desc(Date)) %>% 
  filter(Test == "Blood Pressure") %>%
  head(1)
  
currentBP = paste0(last_bp$Value, " ", last_bp$Units )

valueBox(value = currentBP, icon = "fas fa-clipboard-list")
```


Rows {.tabset}
-------------------------------------



```{r}
### Plot with gains highlighted
# TODO: add conditional smoothing https://rafalab.github.io/dsbook/smoothing.html
# Weight_v <- data.frame(Vitals) %>%
#   filter(Test == "Weight") %>%
#   rename("Weight" = "Value")
# 
# weighttst <- Weight_v %>% 
#   arrange(Date) %>% 
#   mutate(Weight = as.numeric(Weight)) %>%
#   mutate(previous_weight = lag(Weight, order_by = Date), Date =as.Date(Date)) %>% 
#   #mutate(test = ifelse(is.numeric(Weight),1,0))
#   mutate(Color = ifelse(Weight > previous_weight, "red", "green")) %>%
#   mutate(Color = ifelse(is.na(Color),"black", Color)) %>%
#   # ggplot(aes(x = Date, y= Weight, color = Color))+
#   ggplot(aes(x = Date, y= Weight))+
#     geom_point(shape=1, aes(color = Color))+            # Use hollow circles
#     #geom_smooth( method="lm", linetype = 'blank') +
#     #stat_smooth(data = Weight, aes(x = Date,y = Weight), method="lm", linetype = 'blank') +
#     #geom_line(color="grey")+
#     #geom_smooth() +            # Add a loess smoothed fit curve with confidence region
#     scale_color_identity() +
#     scale_x_date(date_labels = "%Y/%m/%d", date_breaks = "3 month") +
#     scale_y_continuous(limits=c(100, 175)) +
#     labs(x = "Year-Month", y = "Weight (lbs)") +
#     #theme(axis.text.x=element_text(angle=60, hjust=1), legend.title = element_blank(), legend.position = "none" )
#     theme(axis.text.x=element_text(angle=60, hjust=1), 
#           legend.title = element_blank(), 
#           legend.position = "none",
#           panel.border = element_blank(),
#           panel.background = element_blank(),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank()) 
# 
# ggplotly(weighttst) %>% 
#   layout(title = list(text = "Weight, gains in red", y = 0.95),
#      #xaxis = list(showticklabels = FALSE),
#      legend = list(orientation = "h",
#                    y = 0, x = 0))
```

### Trends

```{r}

thy_med<- Medicines %>%
  filter(Treatment == "Hypothyroidism") %>%
  mutate(Medicine = paste0(Medication," - ", Qty), StartDate = as.Date(StartDate), EndDate = as.Date(EndDate)) %>%
  select(StartDate, EndDate,Medicine) 

temp <- Temperature %>% 
  mutate(Date = as.Date(Date)) %>%
  arrange(Date) %>% 
  rename("Value" = "Temp") %>%
  select(Date, Hour, Value) %>%
  mutate(Test = "Temperature F") #%>%
  # Add flag for waking temperatures
  #mutate(Waking_Temp = ifelse( (Hour == 8) | (Hour == 7) | (Hour == 6), "black", "grey"))

vitals_trend <- data.frame(Vitals) %>%
  #filter(Test == "Weight") %>%
  filter(Test %in% c("Weight", "BP systolic pressure (top number)", "BP diastolic pressure (bottom number)")) %>%
  select(Date, Test, Value) %>%
  arrange(Date) %>%
  #filter(!is.null(Value)) %>%
  #filter(is.numeric(as.numeric(Value))) %>%
  #mutate(Value = as.numeric(Value)) %>%
  mutate(Value = as.numeric(as.character(Value))) %>%
  filter(!is.na(Value)) %>%
  unnest(cols = Value)

vitals_trend <- bind_rows(vitals_trend, temp) %>%
  mutate(Hour = ifelse(nchar(Hour) < 1 | is.na(Hour), 0, Hour))

span <- 90

# fit <- with(vitals_trend, # %>% filter(Waking_Temp == "black"), 
#             ksmooth(Date, Temp, kernel = "box", bandwidth = span))
# 
# fit <- data.frame(Date = fit$x, smooth = fit$y) %>%
#   mutate(smooth = as.numeric(smooth)) %>%
#   filter(!is.na(smooth))

# p <- vitals_trend %>% 
#   ggplot(aes(x = Date, y = Value)) +
#     geom_point(size = 1.5, alpha = .5, color = "grey") + 
#   #geom_line(data = fit, aes(Date, smooth), color="salmon") +
#   #geom_smooth(span = 14, color="red")
#    scale_x_date(date_labels = "%Y/%m/%d", date_breaks = "3 month") +
#    #scale_y_continuous(limits=c(100, 175)) +
#    labs(x = "Year-Month", y = "Weight (lbs)") +
#     theme(axis.text.x=element_text(angle=60, hjust=1),
#           legend.title = element_blank(),
#           legend.position = "none",
#           panel.border = element_blank(),
#           panel.background = element_blank(),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank())
# 


p <- vitals_trend %>% 
  mutate(Date = as.Date(Date)) %>%
  arrange(Date, Hour) %>% 
  ggplot(aes(x = Date, y= Value))+
  geom_point(shape=1, aes(text = Test))+            # Use hollow circles
  geom_line(color="black")+
  #geom_hline(aes(yintercept=LL), color = "red", linetype="dashed") + #Add LL
  #geom_hline(aes(yintercept=UL), color = "red", linetype="dashed") + #Add UL
  #geom_hline(aes(yintercept=Optimal), color = "green",size = 0.1, linetype="dashed") + #Add target
  geom_vline(data = thy_med, aes(xintercept=as.numeric(EndDate), text = Medicine), color = "white") + #Add medicine change dates
  geom_vline(data = thy_med, aes(xintercept=as.numeric(StartDate), text = Medicine), color = "white") + #Add medicine change dates
  facet_wrap(~ Test, ncol = 1, scales = "free_y", strip.position = "left") +
  facet_grid(rows = vars(Test), scales = "free_y") +
  labs(x = "", y = "Metric") +
  scale_x_date(date_labels = "%Y/%m/%d", date_breaks = "1 month") +
  # theme(axis.text.x=element_text(angle=60, hjust=1), strip.text.y = element_text(angle = 0)) 
  theme(axis.text.x=element_text(angle=60, hjust=1), strip.text.y = element_text(angle = 0),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())


 m <- list(
    l = 0,
    r = 200,
    b = 0,
    t = 0,
    pad = 20
  )
 
gp <- ggplotly(p, dynamicTicks = TRUE) %>%
  rangeslider() %>%
  layout(hovermode = "x",
  autosize=FALSE    
  ) 


for(i in 2:(length(unique(vitals_trend$Test))+1)){
  k = i*2-2
  
  gp[['x']][['layout']][['annotations']][[i]][['x']] <- 1.05#-0.1 # 2-7
  gp[["x"]][["layout"]][["shapes"]][[k]][["x0"]] <-  225
}

gp[['x']][['layout']][['annotations']][[1]][['x']] <- -0.5
gp %>% layout(margin =m)


```



### Weight measurements trend
```{r}
# TODO: add conditional smoothing https://rafalab.github.io/dsbook/smoothing.html

limits <- Limits %>%
  filter(Name == "Weight")

Weight_v <- data.frame(Vitals) %>%
  filter(Test == "Weight") %>%
  rename("Weight" = "Value") %>%
  mutate(Weight = as.numeric(Weight)) %>%
  arrange(Date) %>% 
  mutate(previous_weight = lag(Weight, order_by = Date), Date =as.Date(Date)) 

span <- 60

fit <- with(Weight_v, 
            ksmooth(Date, Weight, kernel = "box", bandwidth = span))

fit <- data.frame(Date = fit$x, smooth = fit$y) %>%
  mutate(smooth = as.numeric(smooth)) %>%
  filter(!is.na(smooth))

p <- Weight_v %>% #mutate(smooth = fit$y) %>%
  #merge(fit,by=c("Date"), all=TRUE) %>%
  ggplot(aes(Date, Weight)) +
    geom_point(size = 1.5, alpha = .5, color = "grey") + 
  geom_line(data = fit, aes(Date, smooth), color="salmon") +
  geom_hline(yintercept = limits$LL, color="lightblue") +
  geom_hline(yintercept = limits$Optimal, color="lightgreen") +
  geom_hline(yintercept = limits$UL, color="lightblue") +
  #geom_smooth(span = 14, color="red")
   scale_x_date(date_labels = "%Y/%m/%d", date_breaks = "3 month") +
  #scale_y_continuous(limits=c(limits$LL, limits$UL)) +
   #scale_y_continuous(limits=c(100, 175)) +
   labs(x = "Year-Month", y = "Weight (lbs)") +
    theme(axis.text.x=element_text(angle=60, hjust=1),
          legend.title = element_blank(),
          legend.position = "none",
          panel.border = element_blank(),
          panel.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())

ggplotly(p) %>% 
  layout(title = list(text = "Weight Trend (lbs)", y = 0.95),
     #xaxis = list(showticklabels = FALSE),
     legend = list(orientation = "h",
                   y = 0, x = 0))


```


### Temperature 
```{r}
limits <- Limits %>%
  filter(Name == "Temperature")

temp <- Temperature %>% 
  mutate(Date = as.Date(Date)) %>%
  arrange(Date) %>% 
  # Add flag for waking temperatures
  mutate(Waking_Temp = ifelse( (Hour == 8) | (Hour == 7) | (Hour == 6), "black", "grey"))

span <- 90

fit <- with(temp %>% filter(Waking_Temp == "black"), 
            ksmooth(Date, Temp, kernel = "box", bandwidth = span))

fit <- data.frame(Date = fit$x, smooth = fit$y) %>%
  mutate(smooth = as.numeric(smooth)) %>%
  filter(!is.na(smooth))

p <- temp %>% 
  ggplot(aes(x = Date, y = Temp)) +
    geom_point(size = 1.5, alpha = .5, color = "grey") + 
  geom_line(data = fit, aes(Date, smooth), color="salmon") +
  geom_hline(yintercept = limits$LL, color="lightblue") +
  geom_hline(yintercept = limits$Optimal, color="lightgreen") +
  geom_hline(yintercept = limits$UL, color="lightblue") +
  #geom_smooth(span = 14, color="red")
   scale_x_date(date_labels = "%Y/%m/%d", date_breaks = "3 month") +
  #scale_y_continuous(limits=c(limits$LL, limits$UL)) +
   #scale_y_continuous(limits=c(100, 175)) +
   labs(x = "Year-Month", y = "Temperautre (F)") +
    theme(axis.text.x=element_text(angle=60, hjust=1),
          legend.title = element_blank(),
          legend.position = "none",
          panel.border = element_blank(),
          panel.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())

ggplotly(p) %>% 
  layout(title = list(text = "Temperature Trend (F)", y = 0.95),
     #xaxis = list(showticklabels = FALSE),
     legend = list(orientation = "h",
                   y = 0, x = 0))


```


```{r}
# 
# # Define levels to color by Type
# temp_levels = unique(Temperature$Hour)
# Temperature$Hour <- factor(Temperature$Hour, levels=temp_levels, ordered=TRUE)
# 
# # Define colors
# color = brewer.pal(n = length(unique(Temperature$Hour)), name = "RdBu")

# Temperature_v <- data.frame(Vitals) %>%
#   filter(Test == "Temperature") %>%
#   rename("Temp" = "Value") %>%
#   mutate()
# 
# temp <- Temperature %>% 
#   arrange(Date) %>% 
#   # Add flag for waking temperatures
#   mutate(Waking_Temp = ifelse( (Hour == 8) | (Hour == 7) | (Hour == 6), "black", "grey")) %>%
#   # ggplot(aes(x = as.Date(Date), y= Temp, color = Waking_Temp))+
#   ggplot(aes(x = as.Date(Date), y= Temp))+
#   # ggplot(aes(x = as.Date(Date), y= Temp, color = Waking_Temp))+
#     geom_point(shape=1, aes(color = Waking_Temp)) +            # Use hollow circles
#     #geom_line(color="grey")+
#     #stat_smooth(method="lm", aes(color = Waking_Temp)) +
#     #stat_smooth() +
#     #geom_smooth() +            # Add a loess smoothed fit curve with confidence region
#     scale_color_identity() +
#     scale_x_date(date_labels = "%Y/%m/%d", date_breaks = "3 month") +
#     scale_y_continuous(limits=c(95, 105)) +
#     labs(x = "Year-Month", y = "Temp (F)", legend = "Waking Temperature") +
#     #theme(axis.text.x=element_text(angle=60, hjust=1))
#     theme(axis.text.x=element_text(angle=60, hjust=1), 
#           legend.title = element_blank(), 
#           legend.position = "none",
#           panel.border = element_blank(),
#           panel.background = element_blank(),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank()) 
# 
# ggplotly(temp) %>% 
#   layout(title = list(text = "Temperature, waking temp in black", y = 0.95),
#      #xaxis = list(showticklabels = FALSE),
#      legend = list(orientation = "h",
#                    y = 0, x = 0))


```


### Systolic Blood Pressure trend
```{r}
# TODO: add conditional smoothing https://rafalab.github.io/dsbook/smoothing.html
limits <- Limits %>%
  filter(Name == "BP systolic pressure (top number)")

bp_v <- data.frame(Vitals) %>%
  filter(Test == "BP systolic pressure (top number)") %>%
  mutate(Value = as.numeric(Value)) %>%
  arrange(Date) %>% 
  mutate(previous_weight = lag(Value, order_by = Date), Date =as.Date(Date)) 
#rename("BP systolic pressure (top number)" = "Value") %>%

span <- 60

fit <- with(bp_v, 
            ksmooth(Date, Value, kernel = "box", bandwidth = span))

fit <- data.frame(Date = fit$x, smooth = fit$y) %>%
  mutate(smooth = as.numeric(smooth)) %>%
  filter(!is.na(smooth))

p <- bp_v %>% 
  ggplot(aes(Date, Value)) +
    geom_point(size = 1.5, alpha = .5, color = "grey") + 
  geom_line(data = fit, aes(Date, smooth), color="salmon") +
  geom_hline(yintercept = limits$LL, color="lightblue") +
  geom_hline(yintercept = limits$Optimal, color="lightgreen") +
  geom_hline(yintercept = limits$UL, color="lightblue") +
   scale_x_date(date_labels = "%Y/%m/%d", date_breaks = "3 month") +
  #scale_y_continuous(limits=c(limits$LL, limits$UL)) +
   labs(x = "Year-Month", y = "Blood Pressure (mm Hg)") +
    theme(axis.text.x=element_text(angle=60, hjust=1),
          legend.title = element_blank(),
          legend.position = "none",
          panel.border = element_blank(),
          panel.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())

ggplotly(p) %>% 
  layout(title = list(text = "Systolic Blood Pressure (mm Hg)", y = 0.95),
     #xaxis = list(showticklabels = FALSE),
     legend = list(orientation = "h",
                   y = 0, x = 0))


```

### Diastolic Blood Pressure trend
```{r}
# TODO: add conditional smoothing https://rafalab.github.io/dsbook/smoothing.html

limits <- Limits %>%
  filter(Name == "BP diastolic pressure (bottom number)")

bp_v <- data.frame(Vitals) %>%
  filter(Test == "BP diastolic pressure (bottom number)") %>%
  mutate(Value = as.numeric(Value)) %>%
  arrange(Date) %>% 
  mutate(previous_weight = lag(Value, order_by = Date), Date =as.Date(Date)) 
#rename("BP systolic pressure (top number)" = "Value") %>%

span <- 60

fit <- with(bp_v, 
            ksmooth(Date, Value, kernel = "box", bandwidth = span))

fit <- data.frame(Date = fit$x, smooth = fit$y) %>%
  mutate(smooth = as.numeric(smooth)) %>%
  filter(!is.na(smooth))

p <- bp_v %>% 
  ggplot(aes(Date, Value)) +
    geom_point(size = 1.5, alpha = .5, color = "grey") + 
  geom_line(data = fit, aes(Date, smooth), color="salmon") +
  geom_hline(yintercept = limits$LL, color="lightblue") +
  geom_hline(yintercept = limits$Optimal, color="lightgreen") +
  geom_hline(yintercept = limits$UL, color="lightblue") +
   scale_x_date(date_labels = "%Y/%m/%d", date_breaks = "3 month") +
   #scale_y_continuous(limits=c(limits$LL, limits$UL)) +
   labs(x = "Year-Month", y = "Blood Pressure (mm Hg)") +
    theme(axis.text.x=element_text(angle=60, hjust=1),
          legend.title = element_blank(),
          legend.position = "none",
          panel.border = element_blank(),
          panel.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())

ggplotly(p) %>% 
  layout(title = list(text = "BP diastolic pressure (mm Hg)", y = 0.95),
     #xaxis = list(showticklabels = FALSE),
     legend = list(orientation = "h",
                   y = 0, x = 0))

```


### Heart Rate trend
```{r}
# TODO: add conditional smoothing https://rafalab.github.io/dsbook/smoothing.html
limits <- Limits %>%
  filter(Name == "HR")

hr_v <- data.frame(Vitals) %>%
  filter(Test == "HR") %>%
  mutate(Value = as.numeric(Value)) %>%
  arrange(Date) %>% 
  mutate(previous_weight = lag(Value, order_by = Date), Date =as.Date(Date)) 

span <- 60

fit <- with(hr_v, 
            ksmooth(Date, Value, kernel = "box", bandwidth = span))

fit <- data.frame(Date = fit$x, smooth = fit$y) %>%
  mutate(smooth = as.numeric(smooth)) %>%
  filter(!is.na(smooth))

p <- hr_v %>% 
  ggplot(aes(Date, Value)) +
    geom_point(size = 1.5, alpha = .5, color = "grey") + 
  geom_line(data = fit, aes(Date, smooth), color="salmon") +
  geom_hline(yintercept = limits$LL, color="lightblue") +
  geom_hline(yintercept = limits$Optimal, color="lightgreen") +
  geom_hline(yintercept = limits$UL, color="lightblue") +
   scale_x_date(date_labels = "%Y/%m/%d", date_breaks = "3 month") +
   #scale_y_continuous(limits=c(limits$LL, limits$UL)) +
   labs(x = "Year-Month", y = "Heart Rate (bpm)") +
    theme(axis.text.x=element_text(angle=60, hjust=1),
          legend.title = element_blank(),
          legend.position = "none",
          panel.border = element_blank(),
          panel.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank())

ggplotly(p) %>% 
  layout(title = list(text = "Heart Rate (bpm)", y = 0.95),
     #xaxis = list(showticklabels = FALSE),
     legend = list(orientation = "h",
                   y = 0, x = 0))

```



```{r}
#Allergies {data-orientation=columns}
#===================================== 

### Allergen Information

```


Immunizations {data-orientation=columns}
===================================== 

### Vaccination History
```{r}
#Collapse first column if contents repeat
kable(Immunizations %>% arrange(desc(Date)), align = "c") %>%
  kable_styling(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "top")

```


Thyroid {data-orientation=rows}
===================================== 

Rows 
-------------------------------------

### Last thyroid lab panel was on: 

```{r}
thycurrent_lab<- Records %>%
  filter(Type == "Labs") 

thycurrent_lab<- thycurrent_lab %>%
  filter(Date == max(thycurrent_lab$Date, na.rm=T))

thycurrent_lab = paste0(thycurrent_lab$Date)

# Show the number in a special valueBox (note the {.value-box} CSS class
# above—that applies the CSS class to the HTML output and makes it render
# correctly)
valueBox(value = thycurrent_lab, icon = "fas fa-rocket")
```

### Current thyroid medication is: 

```{r}
# TODO: set up multiple line handling 
thycurrent_med<- Medicines %>%
  filter(Treatment == "Hypothyroidism") %>%
  mutate(Medicine = paste0(Medication," - ", Qty), StartDate = as.Date(StartDate), EndDate = as.Date(EndDate)) %>%
  select(StartDate, EndDate,Medicine) 

thycurrent_med<- thycurrent_med %>%
  filter(StartDate == max(thycurrent_med$StartDate, na.rm=T))

thycurrent_med = paste0(thycurrent_med$Medicine, " started on ", thycurrent_med$StartDate, collapse = " ")

# Show the number in a special valueBox (note the {.value-box} CSS class
# above—that applies the CSS class to the HTML output and makes it render
# correctly)
valueBox(value = thycurrent_med, icon = "fas fa-rocket")
```



Rows {.tabset}
-------------------------------------

### Key Thyroid Metrics
```{r}
#Goal show the timeplots for each thyroid metric overlaid with changes in medication

thy_med<- Medicines %>%
  filter(Treatment == "Hypothyroidism") %>%
  mutate(Medicine = paste0(Medication," - ", Qty), StartDate = as.Date(StartDate), EndDate = as.Date(EndDate)) %>%
  select(StartDate, EndDate,Medicine) 

thyroid_plot_data <- Thyroid %>% 
  mutate(Date = as.Date(Date)) %>%
  #mutate(Name = str_wrap(Name, width = 15)) %>%
  arrange(Date) %>% 
  filter(Name %in% c("Free T4 (ng/dL)", "Free T3 (pg/mL)") | grepl("TSH", Name, fixed = TRUE)) 
  
thyroid_plot <- thyroid_plot_data %>%  
  ggplot(aes(x = Date, y= Value))+
  geom_point(shape=1, aes(text = Name))+            # Use hollow circles
  geom_line(color="black")+
  geom_hline(aes(yintercept=LL), color = "red", linetype="dashed") + #Add LL
  geom_hline(aes(yintercept=UL), color = "red", linetype="dashed") + #Add UL
  geom_hline(aes(yintercept=Optimal), color = "green",size = 0.1, linetype="dashed") + #Add target
  geom_vline(data = thy_med, aes(xintercept=as.numeric(EndDate), text = Medicine), color = "purple") + #Add medicine change dates
  geom_vline(data = thy_med, aes(xintercept=as.numeric(StartDate), text = Medicine), color = "purple") + #Add medicine change dates
  #facet_wrap(~ Name, ncol = 1, scales = "free_y", strip.position = "left") +
  facet_grid(rows = vars(Name), scales = "free_y") +
  labs(x = "", y = "Metric") +
  scale_x_date(date_labels = "%Y/%m/%d", date_breaks = "1 month") +
  theme(axis.text.x=element_text(angle=60, hjust=1), strip.text.y = element_text(angle = 0)) 

 m <- list(
    l = 0,
    r = 200,
    b = 0,
    t = 0,
    pad = 20
  )
 
gp <- ggplotly(thyroid_plot, dynamicTicks = TRUE) %>%
  rangeslider() %>%
  layout(hovermode = "x",
  autosize=FALSE    
  ) 


for(i in 2:(length(unique(thyroid_plot_data$Name))+1)){
  k = i*2-2
  
  gp[['x']][['layout']][['annotations']][[i]][['x']] <- 1.05#-0.1 # 2-7
  gp[["x"]][["layout"]][["shapes"]][[k]][["x0"]] <-  225
}

gp[['x']][['layout']][['annotations']][[1]][['x']] <- -0.5
gp %>% layout(margin =m)


```

### All Thyroid Metrics
```{r}
#Goal show the timeplots for each thyroid metric overlaid with changes in medication

thy_med<- Medicines %>%
  filter(Treatment == "Hypothyroidism") %>%
  mutate(Medicine = paste0(Medication," - ", Qty), StartDate = as.Date(StartDate), EndDate = as.Date(EndDate)) %>%
  select(StartDate, EndDate,Medicine) 

thyroid_plot <- Thyroid %>% 
  mutate(Date = as.Date(Date)) %>%
  #mutate(Name = str_wrap(Name, width = 15)) %>%
  arrange(Date) %>% 
  ggplot(aes(x = Date, y= Value))+
  geom_point(shape=1, aes(text = Name))+            # Use hollow circles
  geom_line(color="black")+
  geom_hline(aes(yintercept=LL), color = "red", linetype="dashed") + #Add LL
  geom_hline(aes(yintercept=UL), color = "red", linetype="dashed") + #Add UL
  geom_hline(aes(yintercept=Optimal), color = "green",size = 0.1, linetype="dashed") + #Add target
  geom_vline(data = thy_med, aes(xintercept=as.numeric(EndDate), text = Medicine), color = "purple") + #Add medicine change dates
  geom_vline(data = thy_med, aes(xintercept=as.numeric(StartDate), text = Medicine), color = "purple") + #Add medicine change dates
  #facet_wrap(~ Name, ncol = 1, scales = "free_y", strip.position = "left") +
  facet_grid(rows = vars(Name), scales = "free_y") +
  labs(x = "", y = "Metric") +
  scale_x_date(date_labels = "%Y/%m/%d", date_breaks = "1 month") +
  theme(axis.text.x=element_text(angle=60, hjust=1), strip.text.y = element_text(angle = 0)) 

 m <- list(
    l = 0,
    r = 200,
    b = 0,
    t = 0,
    pad = 20
  )
 
gp <- ggplotly(thyroid_plot, dynamicTicks = TRUE) %>%
  rangeslider() %>%
  layout(hovermode = "x",
  autosize=FALSE    
  ) 


for(i in 2:(length(unique(Thyroid$Name))+1)){
  k = i*2-2
  
  gp[['x']][['layout']][['annotations']][[i]][['x']] <- 1.05#-0.1 # 2-7
  gp[["x"]][["layout"]][["shapes"]][[k]][["x0"]] <-  225
}

gp[['x']][['layout']][['annotations']][[1]][['x']] <- -0.5
gp %>% layout(margin =m)


```






Labs {data-orientation=columns}
===================================== 

Column {.tabset}
-------------------------------------

```{r}
# style = "data-width: 100%;"
#https://stackoverflow.com/questions/32841221/add-sparkline-graph-to-a-table
#https://github.com/renkun-ken/formattable/issues/10
#https://stackoverflow.com/questions/43251214/composited-sparkline-in-r-with-dt-and-shiny
#https://timelyportfolio.github.io/dataui/articles/replicate_tufte_example.html
#https://github.com/htmlwidgets/sparkline/issues/3
#https://www.displayr.com/formattable/
#https://stackoverflow.com/questions/32634640/sparkline-r-creating-html-table
#https://stackoverflow.com/questions/42251594/r-combining-data-tables-dt-package-and-sparkline-package-box-plot-with-target-va
#https://www.infoworld.com/article/3318222/how-to-add-sparklines-to-r-tables.html
#https://stackoverflow.com/questions/43251214/composited-sparkline-in-r-with-dt-and-shiny
#https://omnipotent.net/jquery.sparkline/#common
#https://commons.wikimedia.org/wiki/MediaWiki:Gadget-jquery.sparkline.js
#https://wiki.genexus.com/commwiki/servlet/wiki?16752,Sparkline+Control
#https://martinctc.github.io/blog/vignette-downloadable-tables-in-rmarkdown-with-the-dt-package/
#https://github.com/rstudio/flexdashboard/issues/117
#https://groups.google.com/forum/#!topic/shiny-discuss/N5N0PqcBvuY
#https://stackoverflow.com/questions/39775563/r-vertical-scroll-not-working
#https://stackoverflow.com/questions/54244718/combining-sparkline-in-kableextra-table

Labs_plot <- Labs %>%
  rbind(Thyroid) %>%
  #filter(Name %in% c("Ferritin (ng/mL)", "Alkaline Phosphatase (U/L)")) %>%
  arrange(Date) %>%
  mutate(Value = as.numeric(as.character(Value))) %>%
  filter(is.na(Value) != TRUE) %>%
  filter(is.null(Value) != TRUE) %>%
  filter(Value != "NULL") %>%
  mutate( UL = ifelse(is.null(UL) | is.na(UL) | is.nan(UL), Inf, UL ))  %>% #Set limit to inf if no limit
  mutate( LL = ifelse(is.null(LL) | is.na(LL) | is.nan(LL), -Inf, LL ))  %>% #Set limit to inf if no limit  
  # Add flag if measurement came back out of spec
  mutate(OOS = ifelse((Value > UL | Value < LL),1,0)) %>%
  # Add flag if any measurement has ever come back out of spec
  group_by(Name) %>%
  mutate(Monitor = max(OOS)) %>%
  unnest(Value)
  
Labs_plot_tmp <- data.frame()
Labs_plot_out <- data.frame()

for(j in (unique(Labs_plot$Name))){
  #print(j)
  
  Labs_plot_tmp <- Labs_plot %>%
    filter(Name %in% j) %>%
    mutate(
  TrendSparkLine = spk_chr(
                       Value, type= "line", #One of 'line' (default), 'bar', 'tristate', 'discrete', 'bullet', 'pie' or 'box'
                       # valueSpots = .$Value, 
                       fillColor = FALSE, # "defaults to #cdf"
                       normalRangeMin = min(unlist(.$LL)),
                       normalRangeMax = max(unlist(.$UL)),
                       normalRangeColor = "#cdf", #'lightgreen', #'#cdf"'
                       lineWidth =5,
                       # #drawNormalOnTop = TRUE,
                       spotRadius = 5,
                       spotColor = 'orange',
                       maxSpotColor = 'orange',
                       minSpotColor = 'orange',
                       defaultPixelsPerValue = 10# defaults to 3 per value
                       ),
  #   TrendDiscrete_Low = spk_chr(
  #                      Value, type= "discrete", #One of 'line' (default), 'bar', 'tristate', 'discrete', 'bullet', 'pie' or 'box'
  #                      thresholdValue = min(unlist(.$LL)),
  #                      thresholdColor = "red", #"#00f", # Color underneath the threshold
  #                      lineColor = "green", # Color over the threshold
  #                      lineWidth= 3 #defaults to 1
  #                      ),
  # TrendDiscrete_High = spk_chr(
  #                      Value, type= "discrete", #One of 'line' (default), 'bar', 'tristate', 'discrete', 'bullet', 'pie' or 'box'
  #                      thresholdValue = max(unlist(.$UL)),
  #                      thresholdColor = "green", #"#00f", # Color underneath the threshold
  #                      lineColor = "red", # Color over the threshold
  #                      lineWidth= 3 #defaults to 1
  #                      ),
  # TrendBox = spk_chr(
  #                      Value, type= "box", #One of 'line' (default), 'bar', 'tristate', 'discrete', 'bullet', 'pie' or 'box'
  #                      showOutliers = TRUE
  #                      ),
      ) %>%
  arrange(desc(Date)) %>%
  mutate(Value =as.numeric(Value)) %>% #Make sure that everything is converted to a number
  filter(is.na(Value) != TRUE) %>%
  slice(1) %>% # Show most recent result only
  select(-Note, -Optimal) 
  
  if(nrow(Labs_plot_out)<1){
    Labs_plot_out <- Labs_plot_tmp
  } else{
    Labs_plot_out <- rbind(Labs_plot_out, Labs_plot_tmp)
  }
  
}



```

### Current
```{r}
out_current <- Labs_plot_out %>%
arrange(Category, Name) %>%
#filter(OOS == 1) %>%
# filter(Date >= Sys.Date()-365) %>%
filter(Date == max(Labs_plot_out$Date)) %>%  
mutate( UL = ifelse(is.null(UL) | is.na(UL) | is.nan(UL), Inf, UL ))  %>% #Set limit to inf if no limit
mutate( LL = ifelse(is.null(LL) | is.na(LL) | is.nan(LL), -Inf, LL ))  %>% #Set limit to inf if no limit  
mutate( Value = cell_spec(Value, "html", color = ifelse((Value > UL | Value < LL), "red", "green"))) %>% #Color if OOS      
  formattable::format_table(
  x = .,
  formatters = list(
    align=c("l")
  )
) %>%
  kable_styling("striped", full_width = F) %>%
  htmltools::HTML() %>%
  shiny::div() %>%
  sparkline::spk_add_deps()

out_current
```



### Attention
```{r}
out_attention <- Labs_plot_out %>%
arrange(Category, Name) %>%
filter(OOS == 1) %>%
filter(Date >= Sys.Date()-365) %>%
mutate( UL = ifelse(is.null(UL) | is.na(UL) | is.nan(UL), Inf, UL ))  %>% #Set limit to inf if no limit
mutate( LL = ifelse(is.null(LL) | is.na(LL) | is.nan(LL), -Inf, LL ))  %>% #Set limit to inf if no limit  
mutate( Value = cell_spec(Value, "html", color = ifelse((Value > UL | Value < LL), "red", "green"))) %>% #Color if OOS      
  formattable::format_table(
  x = .,
  formatters = list(
    align=c("l")
  )
) %>%
  kable_styling("striped", full_width = F) %>%
  htmltools::HTML() %>%
  shiny::div() %>%
  sparkline::spk_add_deps()

out_attention
```

### Monitor
```{r}
out_monitor <- Labs_plot_out %>%
arrange(Category, Name) %>%
filter(Monitor == 1) %>%
mutate( UL = ifelse(is.null(UL) | is.na(UL) | is.nan(UL), Inf, UL ))  %>% #Set limit to inf if no limit
mutate( LL = ifelse(is.null(LL) | is.na(LL) | is.nan(LL), -Inf, LL ))  %>% #Set limit to inf if no limit  
mutate( Value = cell_spec(Value, "html", color = ifelse((Value > UL | Value < LL), "red", "green"))) %>% #Color if OOS      
  formattable::format_table(
  x = .,
  formatters = list(
    align=c("l")
  )
) %>%
  kable_styling("striped", full_width = F) %>%
  htmltools::HTML() %>%
  shiny::div() %>%
  sparkline::spk_add_deps()

out_monitor
```

### All
```{r}
out <- Labs_plot_out %>%
arrange(Category, Name) %>%
mutate( UL = ifelse(is.null(UL) | is.na(UL) | is.nan(UL), Inf, UL ))  %>% #Set limit to inf if no limit
mutate( LL = ifelse(is.null(LL) | is.na(LL) | is.nan(LL), -Inf, LL ))  %>% #Set limit to inf if no limit  
mutate( Value = cell_spec(Value, "html", color = ifelse((Value > UL | Value < LL), "red", "green"))) %>% #Color if OOS      
  formattable::format_table(
  x = .,
  formatters = list(
    align=c("l")
  )
) %>%
  kable_styling("striped", full_width = F) %>%
  htmltools::HTML() %>%
  shiny::div() %>%
  sparkline::spk_add_deps()

out
```


### Individual Trends
```{r}
# TODO: add conditional smoothing https://rafalab.github.io/dsbook/smoothing.html

Labs_plot_tochart <- Labs_plot %>%
#filter(Name %in% c("Ferritin (ng/mL)", "Alkaline Phosphatase (U/L)")) %>%
mutate(Date = as.Date(Date, format = "%m/%d/%Y"))

#Fixing known plotly error with knitr
l <- htmltools::tagList()

tests <- unique(Labs_plot$Name)

# for(q in unique(Labs_plot$Name)){
for(i in 1:length(tests) ){
  q = tests[i]
  #q="Ferritin (ng/mL)"
  Labs_charts <- Labs_plot_tochart  %>%
    filter(Name %in% c(q)) %>%
    arrange(Date) 

  limits <- Limits %>%
    filter(Name == q)

  span <- 60

  fit <- with(Labs_charts, 
              ksmooth(Date, Value, kernel = "box", bandwidth = span))

  fit <- data.frame(Date = fit$x, smooth = fit$y) %>%
    mutate(smooth = as.numeric(smooth)) %>%
    filter(!is.na(smooth))

  p <- Labs_charts %>% #mutate(smooth = fit$y) %>%
    mutate(Color = ifelse(OOS < 1, "grey", "salmon")) %>%
    ggplot(aes(Date, Value, color = Color)) +
    geom_point(size = 1.5, alpha = .5) + 
    scale_color_identity() +
    #geom_line(color="grey")+
    {if(is.numeric(limits$LL)) geom_hline(yintercept = limits$LL, color="lightblue") } + 
    {if(is.numeric(limits$Optimal)) geom_hline(yintercept = limits$Optimal, color="lightgreen")} +
    {if(is.numeric(limits$UL)) geom_hline(yintercept = limits$UL, color="lightblue")} +
    geom_line(data = fit, aes(Date, smooth), color="grey") +
    #geom_smooth(span = 14, color="red")
    scale_x_date(date_labels = "%Y/%m/%d", date_breaks = "3 month") +
    #scale_y_continuous(limits=c(limits$LL, limits$UL)) +
     #scale_y_continuous(limits=c(100, 175)) +
     labs(x = "Year-Month", y = q) +
      theme(axis.text.x=element_text(angle=60, hjust=1),
            legend.title = element_blank(),
            legend.position = "none",
            panel.border = element_blank(),
            panel.background = element_blank(),
            panel.grid.major = element_blank(),
            panel.grid.minor = element_blank()) 
  
  l[[i]] <- ggplotly(p) %>% 
    layout(title = list(text = q, y = 0.95),
       #xaxis = list(showticklabels = FALSE),
       legend = list(orientation = "h",
                     y = 0, x = 0))
  
  #print(plot_out)
}

l

```



 ### Control Charts 
```{r, out.width='100%', fig.width=10, fig.height=4, fig.align="left"}
#, fig.width=15
#out.width = "100%", fig.height = 5
#dpi = 200
# out.width = "100%"
#https://cran.r-project.org/web/packages/ggQC/vignettes/XbarR_HOTTO.html
#https://jmarriott.com/posts/testing-ggqc/
#https://r-bar.net/ggqc-ggplot-quality-control-charts/
#https://stackoverflow.com/questions/54400546/how-to-add-an-histogram-or-density-plot-on-the-right-hand-side-of-this-example-p
#https://stackoverflow.com/questions/7705345/how-can-i-extract-plot-axes-ranges-for-a-ggplot2-object
#https://stackoverflow.com/questions/55248191/if-condition-inside-ggplot?noredirect=1&lq=1
#https://timelyportfolio.github.io/dataui/articles/replicate_tufte_example.html
#https://patchwork.data-imaginist.com/articles/guides/assembly.html

# Labs_spc_raw <- Labs  %>%
#     rbind(Thyroid) %>%
#     #filter(Name %in% c("Ferritin (ng/mL)", "Alkaline Phosphatase (U/L)")) %>%
#     filter(is.na(Value) != TRUE) %>%
#     filter(is.null(Value) != TRUE) %>%
#     filter(Value != "NULL") %>%
#     mutate(Value = as.numeric(Value)) %>%
#     filter(is.na(Value) != TRUE) %>%
#   unique()
# 
# for(q in unique(Labs_spc_raw$Name)){
#   Labs_spc <- Labs_spc_raw  %>%
#     rbind(Thyroid) %>%
#     filter(Name %in% c(q)) %>%
#     arrange(Date)
#   
#   Labs_spc_plot <- Labs_spc %>%
#     arrange(Date) %>%
#     mutate(Run_Number = row_number()) %>%
#     select(Name, Value, Run_Number) %>%
#     rename("Process" = "Name") %>%
#     #mutate(Process = 1,Value =as.numeric(Value)) %>%
#     mutate(Value =as.numeric(Value)) %>%
#     ungroup()
#   
#   LL_flag = is.numeric(min(Labs_spc$LL, na.rm = TRUE)) 
#   UL_flag = is.numeric(max(Labs_spc$UL, na.rm = TRUE)) 
#   
#   if(LL_flag){LL = min(Labs_spc$LL)}
#   if(UL_flag){UL = max(Labs_spc$UL)}
# 
#   y_range <- range(Labs_spc_plot$Value)
#    
#   ### Make the plot
#   XmR_Plot <- 
#     ggplot(Labs_spc_plot, aes(x = Run_Number, y = Value)) + #init ggplot
#     geom_point() + geom_line() + # add the points and lines
#     {if(LL_flag){geom_hline(aes(yintercept=(LL), color = "black"))}} +
#     {if(LL_flag){geom_label(aes(0,LL,label = paste0("LL-",LL)))}} +
#     {if(UL_flag){geom_hline(aes(yintercept=(UL), color = "black"))}} +
#     {if(UL_flag){geom_label(aes(0,UL,label = paste0("UL-",UL)))}} +
#     #if(!is.na(min(Labs_spc$LL))) geom_hline(data = Labs_plot, aes(yintercept=LL), color = "red", linetype="dashed") +  #Add LL
#     stat_QC(method = "XmR",      # specify QC charting method
#             auto.label = T,      # Use Autolabels
#             label.digits = 2,    # Use two digit in the label
#             show.1n2.sigma = T   # Show 1 and two sigma lines
#             ) +  
#     scale_x_continuous( expand =  expand_scale(mult = .15)) +  # Pad the x-axis
#     theme(axis.text.x=element_text(angle=60, hjust=1), legend.title = element_blank(), legend.position = "none" )
#   
#   # Get control chart range 
#   y_range=layer_scales(XmR_Plot)$y$range$range
#   
#   ### Create density plot
#   dens_plot <- ggplot(Labs_spc_plot, aes(x = Value)) +
#     geom_density() +
#     coord_flip() +
#     scale_x_continuous(limits = y_range) +
#     theme(axis.title.y = element_blank(), axis.text.x=element_text(angle=60, hjust=1), legend.title = element_blank(), legend.position = "none" )
#   
#   #y_dens=layer_scales(dens_plot)$x$range$range
#   
#   plot_out = 
#     #XmR_Plot + 
#     #dens_plot + 
#     #gridExtra::tableGrob(Labs_spc %>% select(Date, Value)) +
#     wrap_plots(XmR_Plot, dens_plot, gridExtra::tableGrob(Labs_spc %>% select(Date, Value)) ) +
#     plot_layout(nrow = 1, widths = c(1, 0.4,0.7,0.1)) + 
#     #plot_layout(nrow = 1, widths = c(.8, 0.2, 0.3)) + 
#     plot_annotation(
#   title = paste0(q),
#   #subtitle = paste0("Most recent"),
#   caption = paste0("Data from ",min(Labs_spc$Date), " to ",max(Labs_spc$Date)))
#   
#   print(plot_out)
# }

```



Womens Health {data-orientation=rows}
===================================== 

Row
-------------------------------------
    
    
### Last Period was on: 

```{r}
last_period =  Period %>% 
  arrange(desc(Date)) %>% 
  filter(grepl("eriod",Activity)) %>%
  head(1)
  
lastPeriod = paste0(last_period$Date )

valueBox(value = lastPeriod, icon = "fas fa-clipboard-list")
```

### Last Pap Smear was on: 

```{r}
current_record<- Records %>%
  filter(Type == "PAP") 

current_record<- current_record %>%
  filter(Date == max(current_record$Date, na.rm=T))

current_record = paste0(current_record$Date)

# Show the number in a special valueBox (note the {.value-box} CSS class
# above—that applies the CSS class to the HTML output and makes it render
# correctly)
valueBox(value = current_record, icon = "fas fa-rocket")
```

### Current Birth Control is: 

```{r}
# TODO: set up multiple line handling 
current_med<- Medicines %>%
  filter(Treatment == "Birth Control") %>%
  mutate(Medicine = paste0(Medication," - ", Qty), StartDate = as.Date(StartDate), EndDate = as.Date(EndDate)) %>%
  select(StartDate, EndDate,Medicine) 

current_med<- current_med %>%
  filter(StartDate == max(current_med$StartDate, na.rm=T))

current_med = paste0(current_med$Medicine, collapse = " ")

# Show the number in a special valueBox (note the {.value-box} CSS class
# above—that applies the CSS class to the HTML output and makes it render
# correctly)
valueBox(value = current_med, icon = "fas fa-rocket")
```



Rows {.tabset}
-------------------------------------


### Cycle

```{r, fig.height=4, fig.width=6}
#, out.width="50%"
#, fig.height=3, fig.width=5
#Resources
# https://vietle.info/post/calendarheatmap/
# https://rdrr.io/cran/ggTimeSeries/man/ggplot_calendar_heatmap.html

dummy_row_today <- data.frame(Date = c(Sys.Date()))

if(max(Period$Date) < Sys.Date() ){
  Period<- bind_rows(Period, dummy_row_today)
}

cycle_period =  Period %>% 
  arrange(desc(Date)) %>% 
  #filter(grepl("eriod",Activity)) %>%
  mutate(ValueCol = ifelse(grepl("eriod",Activity), ifelse(grepl("eavy",Activity),3,2), NA),
         DateCol  = Date)



cycle_bc_period = Period %>% 
  arrange(desc(Date)) %>% 
  mutate(ValueCol = ifelse(grepl("eriod",Activity), 3, 0)) %>% # 3 for period, 0 for nuvaring
  mutate()
  
p1 = ggplot_calendar_heatmap(
   cycle_period,
   dayBorderSize = 0.25, dayBorderColour = "black",
   monthBorderSize = 1, monthBorderColour = "black",
   'DateCol',
   'ValueCol'
) + 
  xlab(NULL) + ylab(NULL) + scale_fill_continuous(low = 'pink', high = 'pink', na.value = "grey90",) + 
  facet_wrap(~Year, ncol = 1) + 
  theme( axis.ticks = element_blank(), legend.position = 'none', strip.background = element_blank()) 
  # theme( axis.text = element_blank(), axis.ticks = element_blank(), legend.position = 'none', strip.background = element_blank()) 

p1






```

### Hormones 

```{r}
library(plotly)
library(dplyr)
library(tidyr)
library(lubridate)
library(tidyverse)
library(rCharts)
#install_github('ramnathv/rCharts', force= TRUE)

#https://github.com/timelyportfolio/rCharts_dimple/blob/gh-pages/example_filters_controls_facet.R
#http://timelyportfolio.github.io/rCharts_dimple/filters_controls_facet.html
#https://github.com/ramnathv/rCharts/issues/365
#https://stackoverflow.com/questions/48096600/can-i-make-a-line-plot-with-a-dropdown-menu-in-r-without-using-shiny-or-plotly

# hormones <- Labs_plot %>%
#   filter(Category %in% c("Hormones", "Thyroid"))
# 
# 
# df <- mtcars
# 
# mtcars_long <- mtcars %>%
#   pivot_longer(5:length(mtcars), names_to = "Name", values_to = "Value")
# 
# 
# cols = colnames(df)
# 
# plot <- plot_ly(df,
#                 type = "scatter",
#                 mode = "lines",
#                 x = ~mpg,
#                 # x = ~c,
#                 y= ~df[[cols[[1]]]],
#                 name = cols[[1]])
# 
# 
# 
# for (col in cols[-1]) {
#   plot <- plot %>% add_lines(x = ~mpg, y = df[[col]], name = col, visible = FALSE)
# }
# 
# 
# plot <- plot %>%
#   layout(
#     title = "Dropdown line plot",
#     xaxis = list(title = "x"),
#     yaxis = list(title = "y"),
#     updatemenus = list(
#       list(
#         y = 0.7,
#         ## Add all buttons at once
#         buttons = lapply(cols, function(col) {
#           list(method="restyle",
#                args = list("visible", cols == col),
#                label = col)
#         })
#       )
#     )
#   )
# 
# plot
# 
# plot <- hplot(data = df, x = mpg, y = hp, type = type = c("line",
#                                                           "bubble", "scatter"), group = "Clap", size = "gear")
# 
# h1 <- hPlot(x = "Wr.Hnd", y = "NW.Hnd", data = MASS::survey, type = c("line",
#                                                                       "bubble", "scatter"), group = "Clap", size = "Age")
# h1$print("chart5")



# hair_eye_male <- subset(as.data.frame(HairEyeColor), Sex == "Male")
# n1 <- nPlot(Freq ~ Hair, group = "Eye", data = hair_eye_male, type = "multiBarChart")
# n1$print("chart3")


#https://ramnathv.github.io/rCharts/
#https://stackoverflow.com/questions/48096600/can-i-make-a-line-plot-with-a-dropdown-menu-in-r-without-using-shiny-or-plotly
#https://stackoverflow.com/questions/48096600/can-i-make-a-line-plot-with-a-dropdown-menu-in-r-without-using-shiny-or-plotly
#https://stackoverflow.com/questions/54858338/multiple-lines-traces-for-each-button-in-a-plotly-drop-down-menu-in-r



hormones <- data.frame(Labs_plot,stringsAsFactors=FALSE) %>%
  filter(Category %in% c("Hormones", "Thyroid")) %>%
  select(Date, Name, Value) %>%
  mutate_if(is.list, simplify_all) %>%    # flatten each list element internally 
  unnest(cols = Value) %>%   # expand
  ungroup() %>%
  unique() %>%
  # group_by(Date, Name) %>%
  # count()
  pivot_wider(names_from = Name, values_from = Value, values_fill = list(values = 0)) %>%
  # pivot_wider(names_from = Name, values_from = Value, values_fill = 0) %>%
  # pivot_wider(id_cols = Date, names_from = Name, values_from = Value, values_fill = 0) %>%
  ungroup() #%>%
  #mutate(test = is.null(`Testosterone, Free (pg/mL)`))
  # mutate_if(is.character, 
  #               str_replace_all, pattern = "NULL", replacement = 0) %>%
  # replace(is.null(.), 0)

#df <- hormones  %>% column_to_rownames(var="Date")

df <- hormones  %>% select(-Date,Date)

cols = colnames(df)

plot <- plot_ly(df,
                type = "scatter",
                #mode = "lines",
                mode = "lines+markers",
                #mode = "markers",
                x = ~Date,
                y = ~df[[cols[[1]]]],
                name = cols[[1]])

for (col in cols[-1]) {
  #plot <- plot %>% add_lines(x = ~Date, y = df[[col]], name = col, visible = FALSE)
  # plot <- plot %>% add_markers(x = ~Date, y = df[[col]], name = col, visible = FALSE)
  plot <- plot %>% add_trace(x = ~Date, y = df[[col]], name = col, mode = "lines+markers", visible = FALSE)
}

plot <- plot %>%
  layout(
    title = "Dropdown Plots",
    xaxis = list(title = "Date"),
    # xaxis = list(title = "Date", range = c(min(df$Date), max(df$Date))),
    # xaxis = list(type = "category", title = "Date", range = c(min(df$Date), max(df$Date))),
    yaxis = list(title = "y"),
    updatemenus = list(
      list(
        y = 0.7,
        ## Add all buttons at once
        buttons = lapply(cols, function(col) {
          list(method="restyle",
               args = list("visible", cols == col),
               label = col)
        })
      )
    )
  )

plot

```



Medications {data-orientation=rows}
===================================== 

Row 
-------------------------------------
    
### Current medications

```{r}
kable(Medicines %>% arrange(Treatment) %>% filter(is.na(EndDate)==TRUE) %>% select(-EndDate), align = "c") %>%
  kable_styling(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "top")

```

Row {.tabset}
-------------------------------------

### Plot

```{r}
Medicines_plot <- Medicines %>%
  mutate(EndDate = replace(EndDate, is.na(EndDate), Sys.Date())) %>%
  mutate(Medicine = paste0(Medication," - ", Qty)) %>%
  arrange(StartDate)

timevis_data <- data.frame(
  id = 1:nrow(Medicines_plot),
  content = Medicines_plot$Medicine,
  start = Medicines_plot$StartDate,
  end   = Medicines_plot$EndDate,
  title = Medicines_plot$Medicine,
  group = Medicines_plot$Treatment
)

timeline_groups <- data.frame(
  id = unique(Medicines_plot$Treatment),
  content = unique(Medicines_plot$Treatment)
)

timevis(data = timevis_data, groups = timeline_groups, options = list(editable = FALSE))
# timevis(data = timevis_data, groups = timeline_groups, options = list(editable = FALSE),showZoom = T,fit = TRUE,height = "800px")
```

### Table

```{r}
# Collapse first column if contents repeat
kable(Medicines %>% arrange(Treatment), align = "c") %>%
  kable_styling(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "top")

```


Conditions / Procedures {data-orientation=rows}
===================================== 

Rows {.tabset}
-------------------------------------

### Events

```{r}
History_plot <- History

timevis_data <- data.frame(
  id = 1:nrow(History_plot),
  content = History_plot$Event,
  start = History_plot$Date,
  end   = c(rep(NA,nrow(History_plot))),
  title = History_plot$Description
)
timevis(timevis_data)

```

```{r}
kable(History %>% arrange(Date), align = "c") %>%
  kable_styling(full_width = F) %>%
  column_spec(1, bold = T) 

```



### Test records
```{r}
Records_plot <- Records

# # Define levels to color by Type
# Records_Levels = unique(Records_plot$Type)
# Records_plot$Type <- factor(Records_plot$Type, levels=Records_Levels, ordered=TRUE)
# 
# # Define colors
# color = brewer.pal(n = length(unique(Records_plot$Type)), name = "RdBu")

timevis_data <- data.frame(
  id = 1:nrow(Records_plot),
  content = Records_plot$Type,
  start = Records_plot$Date,
  end   = c(rep(NA,nrow(Records_plot))),
  title = Records_plot$Notes,
  group = Records_plot$Type
)

timeline_groups <- data.frame(
  id = unique(Records_plot$Type),
  content = unique(Records_plot$Type)
)

timevis(data = timevis_data, groups = timeline_groups, options = list(editable = FALSE))
# timevis(data = timevis_data, groups = timeline_groups, options = list(editable = FALSE),showZoom = T,fit = TRUE,height = "800px")

```

Providers
===================================== 

### Doctors
    
```{r}
#Collapse first column if contents repeat
kable(Doctors %>% arrange(Category), align = "c") %>%
  kable_styling(full_width = F) %>%
  column_spec(1, bold = T) %>%
  collapse_rows(columns = 1:2, valign = "top")


```


```{r}
## References
#https://www.andrewheiss.com/blog/2020/01/01/flexdashboard-dynamic-data/
#https://rud.is/b/2019/01/24/quick-hit-automating-production-graphics-uploads-in-r-markdown-documents-with-googledrive/
#https://gargle.r-lib.org/articles/non-interactive-auth.html#project-level-oauth-cache
#https://cran.r-project.org/web/packages/kableExtra/vignettes/awesome_table_in_html.html
#https://benalexkeen.com/creating-a-timeline-graphic-using-r-and-ggplot2/
#https://stackoverflow.com/questions/3611314/calculate-ages-in-r/25450756#25450756
#https://shiny.rstudio.com/gallery/dog-medical-history.html
#https://www.ecanarys.com/Blogs/ArticleID/135/How-to-Host-your-Webpages-on-Google-Drive#:~:text=Now%20you%20can%20drag%20and,in%20the%20bottom%2Dright%20corner.
#https://resources.github.com/whitepapers/github-and-rstudio/

#Renames
#Pastativity
```









